The Unintended Consequences of Energy Reduction

### 2024-02-15 paper/paper.qmd
Added figure captions

![Figure 1](../other/figures/figure1.png)
![Figure 3](../other/figures/figure3.png)
![Figure 4](../other/figures/figure4.png)

>>>>

![Figure 1](../other/figures/figure1.png)
![Figure 2](../other/figures/figure2.png)
![Figure 3](../other/figures/figure3.png)
![Figure 4](../other/figures/figure4.png)
![Figure 5](../other/figures/figure5.png)
